Blame and Coercion: Together Again for the Second Time

### 2019-10-03 paper.tex
update

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{stmaryrd}

@@

\citet{siek2006gradual} introduces gradual typing.

@@

\section{Blame Calculus}

@@

\section{Hyper-coercion}

@@

	\caption{Hyper-coercion}
	\label{fig:HC-syntax}
\end{figure}

The syntax of Hyper-coercion is shown in \figref{fig:HC-syntax}.

@@

@@

\section{Related Work}

\section{Conclusion}

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{stmaryrd}
\usepackage{todonotes}

@@

\todo[inline]{KC: I want to add more citations here}

@@

The structure of this paper is as follows. Section \ref{sec:blame-calculus} 
reviews the state-of-art of $Lazy$ Coercion Calculi. In section 
\ref{sec:hyper-coercion} we present Hyper-coercion. Section \ref{sec:conclude} 
concludes.

\section{Blame Calculus} \label{sec:blame-calculus}

@@

\section{Hyper-coercion} \label{sec:hyper-coercion}

@@

	\caption{$Lazy D$ Hyper-coercion}
	\label{fig:HC-D}
\end{figure}

@@

The syntax of $ Lazy D $ Hyper-coercion is shown in \figref{fig:HC-D}.

@@

\section{Conclusion} \label{sec:conclude}
